---
title: "Class 04"
author: "Jesse Rosner"
date: "2026-09-02"
output: 
  html_document: true
    toc: true
    toc_float: true
    number_sections: true
    code_folding: true
    code_download: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


# Examine a Job Ad

job = list(
  title   = "Research Data Scientist, Magic Eye",
  company = "Google",
  salary  = list(min = 147000, max = 210000)
)
str(job)

#1. The company name.
job[[2]]
#2. The maximum salary.
max_salary = job$salary$max
#3. The maximum salary again, using only [[ ]].
max_salary_alt = job[[3]][[2]]
#4. The names of the elements in job.
names(job)

# Subsetting

##Subsetting a vector

```{r subset_vec}


crashes_by_day = c(2020, 2241, 2327, 2285, 2380, 1866, 1664)
names(crashes_by_day) = c("Mon", "Tue", "Wed", "Thu",
                          "Fri", "Sat", "Sun")
crashes_by_day[2]  

crashes_by_day[c("Wed,"Fri")]
crashes_by_day[c(3,5)]

crashes_by_day[1:5] #only works for elements in a row [doing that by their index]
crashes_by_day[] #Returns all the elements --> no diff than crashes_by_day
```

#importing data in r

## CSV
```{r csvs}
oh_jobs = readr::read_csv("https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23ebf3fb&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1320&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=IHLIDXUSOH&scale=left&cosd=2021-08-28&coed=2026-08-28&line_color=%230073e6&link_values=false&line_style=solid&mark_type=none&mw=3&lw=3&ost=-99999&oet=99999&mma=0&fml=a&fq=Daily%2C%207-Day&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2026-09-02&revision_date=2026-09-02&nd=2020-02-01")

oh_jobs_baser = read.csv("https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23ebf3fb&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1320&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=IHLIDXUSOH&scale=left&cosd=2021-08-28&coed=2026-08-28&line_color=%230073e6&link_values=false&line_style=solid&mark_type=none&mw=3&lw=3&ost=-99999&oet=99999&mma=0&fml=a&fq=Daily%2C%207-Day&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2026-09-02&revision_date=2026-09-02&nd=2020-02-01")

dplyr::glimpse(oh_jobs)
dplyr::glimpse(oh_jobs_baser)


```



